\textbf{The statistical analysis of non-linear longitudinal data in biomedical research using generalized additive models}

### 2021-05-24 Manuscripts/Manuscript by chapters -v1/Full_document.tex
Changed aesthetics, updated manuscript, added missing sections on Appendix.

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The statistical analysis of non-linear longitudinal data in biomedical research using generalized additive models},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{listings}
\newcommand{\passthrough}[1]{#1}
\lstset{defaultdialect=[5.3]Lua}
\lstset{defaultdialect=[x86masm]Assembler}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{lineno}
\usepackage{authblk}

@@

%\lstset{
%  breaklines=true,
%  stringstyle=\ttfamily,
%  backgroundcolor=\color{gray}
%}
\usepackage{placeins}
\usepackage{subfig}
\usepackage{breqn}
\usepackage[font={small}]{caption}
\usepackage{float}
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

A \emph{post hoc} analysis is the statistical test used in conjunction with rm-ANOVA to perform repeated comparisons to estimate a \emph{p-value}, which in turn is used as a measure of significance.
Although it is possible that a \emph{post hoc} analysis of rm-ANOVA is able to find ``significant'' \emph{p-values}( \emph{p}\textless0.05) from non-linear data, the validity of such metric is dependent on how adequate the model fits the data. In other words, \emph{p-values} are valid only if the model and the data have good agreement; if that is not the case, a ``Type III'' error (known as ``model misspecification'') occurs{[}\protect\hyperlink{ref-dennis2019}{17}{]}. For example, model misspecification will occur when a model that is only able to explain linear responses (such as rm-ANOVA) is fitted to data that follows a quadratic trend, thereby causing the resulting \emph{p-values} and parameter estimates to be invalid {[}\protect\hyperlink{ref-wang2019}{18}{]}.

@@

\passthrough{\lstinline!m1<-gam(StO2\_sim\~Group+s(Day,by=Group,k=5,bs="gp"), method='REML',data=dat\_sim!}

@@

One question that might arise at this point is ``what is the fit that an rm-ANOVA model produces for the simulated data?'' The rm-ANOVA model, which corresponds to Equation \eqref{eq:linear-model} is presented in Figure \ref{fig:sim-smooth-plot},C. This is a typical case of model misspecification: The slopes of each group are different, which would lead to a \emph{p-value} indicating significance for the treatment and time effects, but the model is not capturing the changes that occur at days 2 and between days 5 and 7, whereas the GAM model is able to do so (Figure \ref{fig:sim-smooth-plot},B) .

@@

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\hypertarget{ref-roblyer2011}{}%
\CSLLeftMargin{{[}1{]} }
\CSLRightInline{D. Roblyer, S. Ueda, A. Cerussi, W. Tanamai, A. Durkin, R. Mehta, D. Hsiang, J.A. Butler, C. McLaren, W.P. Chen, B. Tromberg, Optical imaging of breast cancer oxyhemoglobin flare correlates with neoadjuvant chemotherapy response one day after starting treatment, Proceedings of the National Academy of Sciences of the United States of America. 108 (2011) 14626--14631. \url{https://doi.org/10.1073/pnas.1013103108}.}

\leavevmode\hypertarget{ref-tank2020}{}%
\CSLLeftMargin{{[}2{]} }
\CSLRightInline{A. Tank, H.M. Peterson, V. Pera, S. Tabassum, A. Leproux, T. O'Sullivan, E. Jones, H. Cabral, N. Ko, R.S. Mehta, B.J. Tromberg, D. Roblyer, Diffuse optical spectroscopic imaging reveals distinct early breast tumor hemodynamic responses to metronomic and maximum tolerated dose regimens, Breast Cancer Research. 22 (2020) 1--10. \url{https://doi.org/doi:10.1186/s13058-020-01262-1}.}

\leavevmode\hypertarget{ref-pavlov2018}{}%
\CSLLeftMargin{{[}3{]} }
\CSLRightInline{M.V. Pavlov, T.I. Kalganova, Y.S. Lyubimtseva, V.I. Plekhanov, G.Y. Golubyatnikov, O.Y. Ilyinskaya, A.G. Orlova, P.V. Subochev, D.V. Safonov, N.M. Shakhova, A.V. Maslennikova, {Multimodal approach in assessment of the response of breast cancer to neoadjuvant chemotherapy}, {Journal of Biomedical Optics}. {23} (2018). \url{https://doi.org/\%7B10.1117/1.JBO.23.9.091410\%7D}.}

\leavevmode\hypertarget{ref-demidov2018}{}%
\CSLLeftMargin{{[}4{]} }
\CSLRightInline{V. Demidov, A. Maeda, M. Sugita, V. Madge, S. Sadanand, C. Flueraru, I.A. Vitkin, {Preclinical longitudinal imaging of tumor microvascular radiobiological response with functional optical coherence tomography}, {Scientific Reports}. {8} (2018). \url{https://doi.org/\%7B10.1038/s41598-017-18635-w\%7D}.}

\leavevmode\hypertarget{ref-ritter2001}{}%
\CSLLeftMargin{{[}5{]} }
\CSLRightInline{G. Ritter, L. Cohen, C. Williams, E. Richards, L. Old, S. Welt, {Serological analysis of human anti-human antibody responses in colon cancer patients treated with repeated doses of humanized monoclonal antibody A33}, {Cancer Research}. {61} (2001) 6851--6859.}

\leavevmode\hypertarget{ref-roth2017}{}%
\CSLLeftMargin{{[}6{]} }
\CSLRightInline{E.M. Roth, A.C. Goldberg, A.L. Catapano, A. Torri, G.D. Yancopoulos, N. Stahl, A. Brunet, G. Lecorps, H.M. Colhoun, {Antidrug Antibodies in Patients Treated with Alirocumab}, {New England Journal of Medicine}. {376} (2017) 1589--1590. \url{https://doi.org/\%7B10.1056/NEJMc1616623\%7D}.}

\leavevmode\hypertarget{ref-jones2018}{}%
\CSLLeftMargin{{[}7{]} }
\CSLRightInline{J.D. Jones, H.E. Ramser, A.E. Woessner, K.P. Quinn, {In vivo multiphoton microscopy detects longitudinal metabolic changes associated with delayed skin wound healing}, {Communications Biology}. {1} (2018). \url{https://doi.org/\%7B10.1038/s42003-018-0206-4\%7D}.}

\leavevmode\hypertarget{ref-skala2010}{}%
\CSLLeftMargin{{[}8{]} }
\CSLRightInline{M.C. Skala, A. Fontanella, L. Lan, J.A. Izatt, M.W. Dewhirst, Longitudinal optical imaging of tumor metabolism and hemodynamics, Journal of Biomedical Optics. 15 (2010). \url{https://doi.org/10.1117/1.3285584}.}

\leavevmode\hypertarget{ref-greening2018}{}%
\CSLLeftMargin{{[}9{]} }
\CSLRightInline{G.J. Greening, K.P. Miller, C.R. Spainhour, M.D. Cato, T.J. Muldoon, {Effects of isoflurane anesthesia on physiological parameters in murine subcutaneous tumor allografts measured via diffuse reflectance spectroscopy}, {Biomedical Optics Express}. {9} (2018) 2871--2886. \url{https://doi.org/\%7B10.1364/BOE.9.002871\%7D}.}

\leavevmode\hypertarget{ref-sio2016}{}%
\CSLLeftMargin{{[}10{]} }
\CSLRightInline{T.T. Sio, P.J. Atherton, B.J. Birckhead, D.J. Schwartz, J.A. Sloan, D.K. Seisler, J.A. Martenson, C.L. Loprinzi, P.C. Griffin, R.F. Morton, J.C. Anders, T.J. Stoffel, R.E. Haselow, R.B. Mowat, M.A.N. Wittich, J.D. Bearden III, R.C. Miller, {Repeated measures analyses of dermatitis symptom evolution in breast cancer patients receiving radiotherapy in a phase 3 randomized trial of mometasone furoate vs placebo (N06C4 {{[}}alliance{]})}, {Supportive Care in Cancer}. {24} (2016) 3847--3855. \url{https://doi.org/\%7B10.1007/s00520-016-3213-3\%7D}.}

\leavevmode\hypertarget{ref-kamstra2015}{}%
\CSLLeftMargin{{[}11{]} }
\CSLRightInline{J.I. Kamstra, P.U. Dijkstra, M. van Leeuwen, J.L.N. Roodenburg, J.A. Langendijk, {Mouth opening in patients irradiated for head and neck cancer: A prospective repeated measures study}, {Oral Oncology}. {51} (2015) 548--555. \url{https://doi.org/\%7B10.1016/j.oraloncology.2015.01.016\%7D}.}

\leavevmode\hypertarget{ref-wagenmakers2008}{}%
\CSLLeftMargin{{[}12{]} }
\CSLRightInline{E.-J. Wagenmakers, M. Lee, T. Lodewyckx, G.J. Iverson, Bayesian versus frequentist inference, in: H. Hoijtink, I. Klugkist, P.A. Boelen (Eds.), Bayesian Evaluation of Informative Hypotheses, Springer New York, New York, NY, 2008: pp. 181--207. \url{https://doi.org/10.1007/978-0-387-09612-4_9}.}

\leavevmode\hypertarget{ref-gueorguieva2004}{}%
\CSLLeftMargin{{[}13{]} }
\CSLRightInline{R. Gueorguieva, J.H. Krystal, {Move over ANOVA - Progress in analyzing repeated-measures data and its reflection in papers published in the archives of general psychiatry}, Archives of General Psychiatry. 61 (2004) 310--317. \url{https://doi.org/10.1001/archpsyc.61.3.310}.}

\leavevmode\hypertarget{ref-schober2018}{}%
\CSLLeftMargin{{[}14{]} }
\CSLRightInline{P. Schober, T.R. Vetter, Repeated measures designs and analysis of longitudinal data: If at first you do not succeed-try, try again, Anesthesia and Analgesia. 127 (2018) 569--575. \url{https://doi.org/10.1213/ane.0000000000003511}.}

\leavevmode\hypertarget{ref-pinheiro2006}{}%
\CSLLeftMargin{{[}15{]} }
\CSLRightInline{J. Pinheiro, D. Bates, {Mixed-effects models in S and S-PLUS}, Springer Science \& Business Media, 2006. https://doi.org/\url{https://doi.org/10.1007/b98882}.}

\leavevmode\hypertarget{ref-vishwanath2009}{}%
\CSLLeftMargin{{[}16{]} }
\CSLRightInline{K. Vishwanath, H. Yuan, W.T. Barry, M.W. Dewhirst, N. Ramanujam, Using optical spectroscopy to longitudinally monitor physiological changes within solid tumors, Neoplasia. 11 (2009) 889--900. \url{https://doi.org/10.1593/neo.09580}.}

\leavevmode\hypertarget{ref-dennis2019}{}%
\CSLLeftMargin{{[}17{]} }
\CSLRightInline{B. Dennis, J.M. Ponciano, M.L. Taper, S.R. Lele, {Errors in Statistical Inference Under Model Misspecification: Evidence, Hypothesis Testing, and AIC}, {Frontiers in Ecology and Evolution}. {7} (2019). \url{https://doi.org/\%7B10.3389/fevo.2019.00372\%7D}.}

\leavevmode\hypertarget{ref-wang2019}{}%
\CSLLeftMargin{{[}18{]} }
\CSLRightInline{B. Wang, Z. Zhou, H. Wang, X.M. Tu, C. Feng, {The p-value and model specification in statistics}, {General Psychiatry}. {32} (2019). \url{https://doi.org/\%7B10.1136/gpsych-2019-100081\%7D}.}

\leavevmode\hypertarget{ref-liu2010}{}%
\CSLLeftMargin{{[}19{]} }
\CSLRightInline{C. Liu, T.P. Cripe, M.-O. Kim, Statistical issues in longitudinal data analysis for treatment efficacy studies in the biomedical sciences, Molecular Therapy. 18 (2010) 1724--1730. \url{https://doi.org/10.1038/mt.2010.127}.}

\leavevmode\hypertarget{ref-halsey2015}{}%
\CSLLeftMargin{{[}20{]} }
\CSLRightInline{L.G. Halsey, D. Curran-Everett, S.L. Vowler, G.B. Drummond, {The fickle P value generates irreproducible results}, {Nature Methods}. {12} (2015) 179--185. \url{https://doi.org/\%7B10.1038/nmeth.3288\%7D}.}

\leavevmode\hypertarget{ref-abdi2010}{}%
\CSLLeftMargin{{[}21{]} }
\CSLRightInline{H. Abdi, {Holm's Sequential Bonferroni Procedure}, Encyclopedia of Research Design. 1 (2010) 1--8. \url{https://doi.org/10.4135/9781412961288.n178}.}

\leavevmode\hypertarget{ref-nakagawa2004}{}%
\CSLLeftMargin{{[}22{]} }
\CSLRightInline{S. Nakagawa, {A farewell to Bonferroni: the problems of low statistical power and publication bias}, {Behavioral Ecology}. {15} (2004) 1044--1045. \url{https://doi.org/\%7B10.1093/beheco/arh107\%7D}.}

\leavevmode\hypertarget{ref-gelman2012}{}%
\CSLLeftMargin{{[}23{]} }
\CSLRightInline{A. Gelman, J. Hill, M. Yajima, {Why We (Usually) Don't Have to Worry About Multiple Comparisons}, {Journal of Research on Educational Effectiveness}. {5} (2012) 189--211. \url{https://doi.org/\%7B10.1080/19345747.2011.618213\%7D}.}

\leavevmode\hypertarget{ref-albers2019}{}%
\CSLLeftMargin{{[}24{]} }
\CSLRightInline{C. Albers, {The problem with unadjusted multiple and sequential statistical testing}, {Nature Communications}. {10} (2019). \url{https://doi.org/\%7B10.1038/s41467-019-09941-0\%7D}.}

\leavevmode\hypertarget{ref-ugrinowitsch2004}{}%
\CSLLeftMargin{{[}25{]} }
\CSLRightInline{C. Ugrinowitsch, G.W. Fellingham, M.D. Ricard, Limitations of ordinary least squares models in analyzing repeated measures data, Medicine and Science in Sports and Exercise. 36 (2004) 2144--2148. \url{https://doi.org/10.1249/01.mss.0000147580.40591.75}.}

>>>>

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The statistical analysis of non-linear longitudinal data in biomedical research using generalized additive models},
  pdfborder={0 0 0},
  breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\usepackage{listings}
\newcommand{\passthrough}[1]{#1}
\lstset{defaultdialect=[5.3]Lua}
\lstset{defaultdialect=[x86masm]Assembler}
\usepackage{longtable,booktabs}
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{lineno}
\usepackage{authblk}

@@

%\lstset{
%  breaklines=true,
%  stringstyle=\ttfamily,
%  backgroundcolor=\color{gray}
%}
\usepackage{placeins}
\usepackage{subfig}
\usepackage{breqn}
\usepackage[font={small}]{caption}
\usepackage{float}

@@

A \emph{post hoc} analysis is the statistical test used in conjunction with rm-ANOVA to perform repeated comparisons to estimate a \emph{p-value}, which in turn is used as a measure of significance.
Although it is possible that a \emph{post hoc} analysis of rm-ANOVA is able to find ``significant'' \emph{p-values}( \emph{p}\textless{}0.05) from non-linear data, the validity of such metric is dependent on how adequate the model fits the data. In other words, \emph{p-values} are valid only if the model and the data have good agreement; if that is not the case, a ``Type III'' error (known as ``model misspecification'') occurs{[}\protect\hyperlink{ref-dennis2019}{17}{]}. For example, model misspecification will occur when a model that is only able to explain linear responses (such as rm-ANOVA) is fitted to data that follows a quadratic trend, thereby causing the resulting \emph{p-values} and parameter estimates to be invalid {[}\protect\hyperlink{ref-wang2019}{18}{]}.

@@

\passthrough{\lstinline!m1<-gam(StO2\_sim\~Group+s(Day,by=Group,k=5,bs="gp"), method='REML',data=dat\_sim)!}

@@

One question that might arise at this point is ``what is the fit that an rm-ANOVA model produces for the simulated data?''. The rm-ANOVA model, which corresponds to Equation \eqref{eq:linear-model} is presented in Figure \ref{fig:sim-smooth-plot},C. This is a typical case of model misspecification: The slopes of each group are different, which would lead to a \emph{p-value} indicating significance for the treatment and time effects, but the model is not capturing the changes that occur at days 2 and between days 5 and 7, whereas the GAM model is able to do so (Figure \ref{fig:sim-smooth-plot},B) .

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-roblyer2011}{}%
{[}1{]} D. Roblyer, S. Ueda, A. Cerussi, W. Tanamai, A. Durkin, R. Mehta, D. Hsiang, J.A. Butler, C. McLaren, W.P. Chen, B. Tromberg, Optical imaging of breast cancer oxyhemoglobin flare correlates with neoadjuvant chemotherapy response one day after starting treatment, Proceedings of the National Academy of Sciences of the United States of America. 108 (2011) 14626--14631. \url{https://doi.org/10.1073/pnas.1013103108}.

\leavevmode\hypertarget{ref-tank2020}{}%
{[}2{]} A. Tank, H.M. Peterson, V. Pera, S. Tabassum, A. Leproux, T. O'Sullivan, E. Jones, H. Cabral, N. Ko, R.S. Mehta, B.J. Tromberg, D. Roblyer, Diffuse optical spectroscopic imaging reveals distinct early breast tumor hemodynamic responses to metronomic and maximum tolerated dose regimens, Breast Cancer Research. 22 (2020) 1--10. \url{https://doi.org/doi:10.1186/s13058-020-01262-1}.

\leavevmode\hypertarget{ref-pavlov2018}{}%
{[}3{]} M.V. Pavlov, T.I. Kalganova, Y.S. Lyubimtseva, V.I. Plekhanov, G.Y. Golubyatnikov, O.Y. Ilyinskaya, A.G. Orlova, P.V. Subochev, D.V. Safonov, N.M. Shakhova, A.V. Maslennikova, Multimodal approach in assessment of the response of breast cancer to neoadjuvant chemotherapy, Journal of Biomedical Optics. 23 (n.d.). \href{https://doi.org/\%7B10.1117/1.JBO.23.9.091410\%7D}{https://doi.org/\{10.1117/1.JBO.23.9.091410\}}.

\leavevmode\hypertarget{ref-demidov2018}{}%
{[}4{]} V. Demidov, A. Maeda, M. Sugita, V. Madge, S. Sadanand, C. Flueraru, I.A. Vitkin, Preclinical longitudinal imaging of tumor microvascular radiobiological response with functional optical coherence tomography, Scientific Reports. 8 (n.d.). \href{https://doi.org/\%7B10.1038/s41598-017-18635-w\%7D}{https://doi.org/\{10.1038/s41598-017-18635-w\}}.

\leavevmode\hypertarget{ref-ritter2001}{}%
{[}5{]} G. Ritter, L. Cohen, C. Williams, E. Richards, L. Old, S. Welt, Serological analysis of human anti-human antibody responses in colon cancer patients treated with repeated doses of humanized monoclonal antibody A33, Cancer Research. 61 (n.d.) 6851--6859.

\leavevmode\hypertarget{ref-roth2017}{}%
{[}6{]} E.M. Roth, A.C. Goldberg, A.L. Catapano, A. Torri, G.D. Yancopoulos, N. Stahl, A. Brunet, G. Lecorps, H.M. Colhoun, Antidrug Antibodies in Patients Treated with Alirocumab, New England Journal of Medicine. 376 (n.d.) 1589--1590. \href{https://doi.org/\%7B10.1056/NEJMc1616623\%7D}{https://doi.org/\{10.1056/NEJMc1616623\}}.

\leavevmode\hypertarget{ref-jones2018}{}%
{[}7{]} J.D. Jones, H.E. Ramser, A.E. Woessner, K.P. Quinn, In vivo multiphoton microscopy detects longitudinal metabolic changes associated with delayed skin wound healing, Communications Biology. 1 (n.d.). \href{https://doi.org/\%7B10.1038/s42003-018-0206-4\%7D}{https://doi.org/\{10.1038/s42003-018-0206-4\}}.

\leavevmode\hypertarget{ref-skala2010}{}%
{[}8{]} M.C. Skala, A. Fontanella, L. Lan, J.A. Izatt, M.W. Dewhirst, Longitudinal optical imaging of tumor metabolism and hemodynamics, Journal of Biomedical Optics. 15 (2010). \url{https://doi.org/10.1117/1.3285584}.

\leavevmode\hypertarget{ref-greening2018}{}%
{[}9{]} G.J. Greening, K.P. Miller, C.R. Spainhour, M.D. Cato, T.J. Muldoon, Effects of isoflurane anesthesia on physiological parameters in murine subcutaneous tumor allografts measured via diffuse reflectance spectroscopy, Biomedical Optics Express. 9 (n.d.) 2871--2886. \href{https://doi.org/\%7B10.1364/BOE.9.002871\%7D}{https://doi.org/\{10.1364/BOE.9.002871\}}.

\leavevmode\hypertarget{ref-sio2016}{}%
{[}10{]} T.T. Sio, P.J. Atherton, B.J. Birckhead, D.J. Schwartz, J.A. Sloan, D.K. Seisler, J.A. Martenson, C.L. Loprinzi, P.C. Griffin, R.F. Morton, J.C. Anders, T.J. Stoffel, R.E. Haselow, R.B. Mowat, M.A.N. Wittich, J.D. Bearden III, R.C. Miller, Repeated measures analyses of dermatitis symptom evolution in breast cancer patients receiving radiotherapy in a phase 3 randomized trial of mometasone furoate vs placebo (N06C4 {[}alliance{]}), Supportive Care in Cancer. 24 (n.d.) 3847--3855. \href{https://doi.org/\%7B10.1007/s00520-016-3213-3\%7D}{https://doi.org/\{10.1007/s00520-016-3213-3\}}.

\leavevmode\hypertarget{ref-kamstra2015}{}%
{[}11{]} J.I. Kamstra, P.U. Dijkstra, M. van Leeuwen, J.L.N. Roodenburg, J.A. Langendijk, Mouth opening in patients irradiated for head and neck cancer: A prospective repeated measures study, Oral Oncology. 51 (n.d.) 548--555. \href{https://doi.org/\%7B10.1016/j.oraloncology.2015.01.016\%7D}{https://doi.org/\{10.1016/j.oraloncology.2015.01.016\}}.

\leavevmode\hypertarget{ref-wagenmakers2008}{}%
{[}12{]} E.-J. Wagenmakers, M. Lee, T. Lodewyckx, G.J. Iverson, Bayesian versus frequentist inference, in: H. Hoijtink, I. Klugkist, P.A. Boelen (Eds.), Bayesian Evaluation of Informative Hypotheses, Springer New York, New York, NY, 2008: pp. 181--207. \url{https://doi.org/10.1007/978-0-387-09612-4_9}.

\leavevmode\hypertarget{ref-gueorguieva2004}{}%
{[}13{]} R. Gueorguieva, J.H. Krystal, Move over ANOVA - Progress in analyzing repeated-measures data and its reflection in papers published in the archives of general psychiatry, Archives of General Psychiatry. 61 (2004) 310--317. \url{https://doi.org/10.1001/archpsyc.61.3.310}.

\leavevmode\hypertarget{ref-schober2018}{}%
{[}14{]} P. Schober, T.R. Vetter, Repeated measures designs and analysis of longitudinal data: If at first you do not succeed-try, try again, Anesthesia and Analgesia. 127 (2018) 569--575. \url{https://doi.org/10.1213/ane.0000000000003511}.

\leavevmode\hypertarget{ref-pinheiro2006}{}%
{[}15{]} J. Pinheiro, D. Bates, Mixed-effects models in S and S-PLUS, Springer Science \& Business Media, 2006. \url{https://doi.org/https://doi.org/10.1007/b98882}.

\leavevmode\hypertarget{ref-vishwanath2009}{}%
{[}16{]} K. Vishwanath, H. Yuan, W.T. Barry, M.W. Dewhirst, N. Ramanujam, Using optical spectroscopy to longitudinally monitor physiological changes within solid tumors, Neoplasia. 11 (2009) 889--900. \url{https://doi.org/10.1593/neo.09580}.

\leavevmode\hypertarget{ref-dennis2019}{}%
{[}17{]} B. Dennis, J.M. Ponciano, M.L. Taper, S.R. Lele, Errors in Statistical Inference Under Model Misspecification: Evidence, Hypothesis Testing, and AIC, Frontiers in Ecology and Evolution. 7 (n.d.). \href{https://doi.org/\%7B10.3389/fevo.2019.00372\%7D}{https://doi.org/\{10.3389/fevo.2019.00372\}}.

\leavevmode\hypertarget{ref-wang2019}{}%
{[}18{]} B. Wang, Z. Zhou, H. Wang, X.M. Tu, C. Feng, The p-value and model specification in statistics, General Psychiatry. 32 (n.d.). \href{https://doi.org/\%7B10.1136/gpsych-2019-100081\%7D}{https://doi.org/\{10.1136/gpsych-2019-100081\}}.

\leavevmode\hypertarget{ref-liu2010}{}%
{[}19{]} C. Liu, T.P. Cripe, M.-O. Kim, Statistical issues in longitudinal data analysis for treatment efficacy studies in the biomedical sciences, Molecular Therapy. 18 (2010) 1724--1730. \url{https://doi.org/10.1038/mt.2010.127}.

\leavevmode\hypertarget{ref-halsey2015}{}%
{[}20{]} L.G. Halsey, D. Curran-Everett, S.L. Vowler, G.B. Drummond, The fickle P value generates irreproducible results, Nature Methods. 12 (n.d.) 179--185. \href{https://doi.org/\%7B10.1038/nmeth.3288\%7D}{https://doi.org/\{10.1038/nmeth.3288\}}.

\leavevmode\hypertarget{ref-abdi2010}{}%
{[}21{]} H. Abdi, Holm's Sequential Bonferroni Procedure, Encyclopedia of Research Design. 1 (2010) 1--8. \url{https://doi.org/10.4135/9781412961288.n178}.

\leavevmode\hypertarget{ref-nakagawa2004}{}%
{[}22{]} S. Nakagawa, A farewell to Bonferroni: the problems of low statistical power and publication bias, Behavioral Ecology. 15 (n.d.) 1044--1045. \href{https://doi.org/\%7B10.1093/beheco/arh107\%7D}{https://doi.org/\{10.1093/beheco/arh107\}}.

\leavevmode\hypertarget{ref-gelman2012}{}%
{[}23{]} A. Gelman, J. Hill, M. Yajima, Why We (Usually) Don't Have to Worry About Multiple Comparisons, Journal of Research on Educational Effectiveness. 5 (n.d.) 189--211. \href{https://doi.org/\%7B10.1080/19345747.2011.618213\%7D}{https://doi.org/\{10.1080/19345747.2011.618213\}}.

\leavevmode\hypertarget{ref-albers2019}{}%
{[}24{]} C. Albers, The problem with unadjusted multiple and sequential statistical testing, Nature Communications. 10 (n.d.). \href{https://doi.org/\%7B10.1038/s41467-019-09941-0\%7D}{https://doi.org/\{10.1038/s41467-019-09941-0\}}.

\leavevmode\hypertarget{ref-ugrinowitsch2004}{}%
{[}25{]} C. Ugrinowitsch, G.W. Fellingham, M.D. Ricard, Limitations of ordinary least squares models in analyzing repeated measures data, Medicine and Science in Sports and Exercise. 36 (2004) 2144--2148. \url{https://doi.org/10.1249/01.mss.0000147580.40591.75}.

\leavevmode\hypertarget{ref-huynh1976}{}%
{[}26{]} H. Huynh, L.S. Feldt, Estimation of the box correction for degrees of freedom from sample data in randomized block and split-plot designs, Journal of Educational Statistics. 1 (1976) 69--82. \url{https://doi.org/10.3102/10769986001001069}.

\leavevmode\hypertarget{ref-greenhouse1959}{}%
{[}27{]} S.W. Greenhouse, S. Geisser, On methods in the analysis of profile data, Psychometrika. 24 (1959) 95--112. \url{https://doi.org/10.1007/bf02289823}.

\leavevmode\hypertarget{ref-haverkamp2017}{}%
{[}28{]} N. Haverkamp, A. Beauducel, Violation of the Sphericity Assumption and Its Effect on Type-I Error Rates in Repeated Measures ANOVA and Multi-Level Linear Models (MLM), Frontiers in Psychology. 8 (n.d.). \href{https://doi.org/\%7B10.3389/fpsyg.2017.01841\%7D}{https://doi.org/\{10.3389/fpsyg.2017.01841\}}.
